Reach OPT MSNA 2021

### 2021-07-04 MSNA_2021_Monitoring_report.Rmd
Update on the dashboard
Update on the monitoring script.

interview_method_wide
### Interview method Westbank

@@

@@

@@

## Productivity

@@

```{r eval=TRUE, echo=FALSE, results='asis'}
kable(enumerator_productivity_final)%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
```

>>>>

interview_method_wide <- rename(interview_method_wide, "Number_of_interviews" = "in_person")
### Interview method Westbank

@@

enum_productivity <- df %>% 
  filter(df$consent == "yes") %>% 
  group_by(Enumerator = enumerator_num) %>% 
  summarise(Interviews = n()) %>% 
  arrange(desc(Interviews), .by_group = T)

@@

## Enumerator Progress

@@

@@

```{r eval=TRUE, echo=FALSE, results='asis'}
kable(enum_productivity)%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
```
